### 2024-11-21 paper/overview.tex
Add mechanized specification explanation

% Overview explanation
In this chapter, we explain the overall approach to generating multiple
artifacts from the specification and ensuring the correctness of the
specification. \Cref{fig:overview} illustrates an overview of our approach.
% DSL
SpecTec provides a domain-specific language (DSL) for writing specifications.
It is a declarative language designed to resemble the formal notation while
offering a compact and user-friendly syntax.
The code below shows the specification for the \texttt{testop} instruction
written in the DSL:
\begin{lstlisting}[escapechar=\%]
  rule Step_pure/testop:
  (CONST nt c_1) (TESTOP nt testop)  %$\tildecode$%>  (CONST I32 c)
  -- if c = %$\dollarcode$%testop_(nt, testop, c_1)
\end{lstlisting}
The DSL is type checked to prevent meta-level errors such as notation misuses and
dimension mismatches.
Using the DSL, SpecTec generates LaTeX code and mechanized definitions for theorem provers.

@@

>>>>

% Overview explanation
In this chapter, we explain the overall approach to generating multiple
artifacts from the specification and ensuring the correctness of the
specification.
\Cref{fig:overview} illustrates an overview of our approach.
% SpecTec: specification mechanization tool
SpecTec is a tool for \textit{mechanizing} WebAssembly specification
~\cite{spectec}.
Specification mechanization is a technique that treats a specification as data
that can be manipulated by a machine to automatically generate parser and
interpreter ~\cite{jiset}, to generate tests and perform differential tests
~\cite{jest}, to find meta-level errors in the specification ~\cite{jstar}, and
to perform meta-level static analysis for the static analysis of the defined
language ~\cite{jsaver}.
This technique is especially crucial in growing languages such as JavaScript
and WebAssembly.

% DSL
SpecTec provides a domain-specific language (DSL) for writing specifications.
It is a declarative language designed to resemble the formal notation while
offering a compact and user-friendly syntax.
The code below shows the specification for the \texttt{testop} instruction
written in the DSL:
\begin{lstlisting}[escapechar=\%]
  rule Step_pure/testop:
  (CONST nt c_1) (TESTOP nt testop)  %$\tildecode$%>  (CONST I32 c)
  -- if c = %$\dollarcode$%testop_(nt, testop, c_1)
\end{lstlisting}
The DSL is type checked to prevent meta-level errors such as notation misuses and
dimension mismatches.
Using the DSL, SpecTec generates LaTeX code and mechanized definitions for theorem provers.

@@

\red{(Explanation for each chapter for SpecTec)}
